\subsection*{Appendix B: Term-by-term expansion of the Podolsky operator, with every derivative}

Section~4 quantized the classical Hamiltonian (3.22) by expressing the flat-space Laplacian in the ro-vibrational chart [the metric (4.15)] and reweighting to the Watson measure --- i.e.\ by ordering Podolsky's sandwich (4.32$'$). This appendix supplies what the main text compressed: the expansion of the quantized kernel of (4.41),
\begin{equation}
\hat T_{\mathrm{kernel}}=\tfrac12\sum_{\alpha\beta}\hat A_\alpha\,\mu_{\alpha\beta}(Q)\,\hat A_\beta,\qquad
\hat A_\alpha\equiv\hat J_\alpha-\hat L_\alpha-\hat\pi_\alpha,\qquad
\hat L_\alpha\equiv\hat L_{\mathrm{elec},\alpha}, \tag{B.1}
\end{equation}
into its nine products, with \emph{every} coordinate derivative written out and the Hermiticity of each block verified from first principles. All arguments use only: the adjoint of a product reverses the order, $(\hat X\hat Y)^{\dagger}=\hat Y^{\dagger}\hat X^{\dagger}$; integration by parts on the measure $d\mu_W$; and the product rule. No commutator algebra of body-fixed angular momenta appears anywhere (cf.\ the Remark in \S\,4.11). Repeated Cartesian indices $\alpha,\beta\in\{1,2,3\}$ and mode indices $b,c\in\{1,\dots,f\}$ are summed.

\subsubsection*{B.1\quad Toolkit}

The three momentum-like operators live in three separate coordinate sectors:
\begin{equation}
\hat J_\alpha=-i\hbar\,(\mathsf E^{-1})_{s\alpha}\partial_{\Omega_s}\ \ \text{[eq.~(4.24), Euler angles]},\quad
\hat P_b=-i\hbar\,\partial_{Q_b}\ \ \text{[modes]},\quad
\hat L_\alpha=-i\hbar\,\epsilon_{\alpha\beta\gamma}\textstyle\sum_i\bar r_{i\beta}\partial_{\bar r_{i\gamma}}\ \ \text{[electrons]}. \tag{B.2}
\end{equation}
Because they differentiate disjoint sets of variables, \emph{operators from different sectors commute}, and each sector's functions are constants for the other sectors' derivatives. Each is Hermitian on its factor of $d\mu_W$: $\hat J_\alpha$ on $\sin\theta\,d\Omega$ by the divergence identity (4.26) [via (4.27)], $\hat L_\alpha$ on the flat electron measure by (4.18), and $\hat P_b$ on the flat $\prod_bdQ_b$ trivially. The only non-commutativity in the problem is the product rule within the $Q$-sector,
\begin{equation}
\hat P_b\,f(Q)=f(Q)\,\hat P_b-i\hbar\,(\partial_{Q_b}f)
\qquad\Longrightarrow\qquad
\hat P_b\,\mu_{\alpha\beta}=\mu_{\alpha\beta}\hat P_b-i\hbar\,\partial_b\mu_{\alpha\beta},\quad
\hat P_b\,\sigma_{\alpha c}=\sigma_{\alpha c}\hat P_b-i\hbar\,\zeta^{\alpha}_{bc}, \tag{B.3}
\end{equation}
where the last relation uses $\sigma_{\alpha b}=\sum_a\zeta^{\alpha}_{ab}Q_a$ [(3.17a)], linear in $Q$ with \emph{constant} $\zeta^{\alpha}_{ab}=\bigl(\sum_j\mathbf l_{ja}\times\mathbf l_{jb}\bigr)_\alpha$, so $\partial_{Q_b}\sigma_{\alpha c}=\zeta^{\alpha}_{bc}$. The antisymmetry of the cross product gives the sum rule that recurs throughout:
\begin{equation}
\zeta^{\alpha}_{ab}=-\zeta^{\alpha}_{ba}\qquad\Longrightarrow\qquad
\zeta^{\alpha}_{bb}=0,\qquad \sum_b\partial_{Q_b}\sigma_{\alpha b}=\sum_b\zeta^{\alpha}_{bb}=0 . \tag{B.4}
\end{equation}
\textbf{$\hat\pi_\alpha$ is Hermitian on the flat mode measure.} With $\hat\pi_\alpha=\sum_b\sigma_{\alpha b}\hat P_b$, take the adjoint (order reverses; $\sigma$ real, $\hat P_b$ Hermitian), then slide $\hat P_b$ back to the right with (B.3), then apply (B.4):
\begin{equation}
\hat\pi_\alpha^{\dagger}
=\sum_b\hat P_b\,\sigma_{\alpha b}
=\sum_b\bigl(\sigma_{\alpha b}\hat P_b-i\hbar\,\zeta^{\alpha}_{bb}\bigr)
=\hat\pi_\alpha . \tag{B.5}
\end{equation}
Had $\sum_b\zeta^\alpha_{bb}$ been nonzero, $\hat\pi_\alpha$ would have required explicit symmetrization; the antisymmetry of $\zeta$ spares us. Finally, $\mu_{\alpha\beta}(Q)=\mu_{\beta\alpha}(Q)$ is a real symmetric function of $Q$ alone.

\subsubsection*{B.2\quad The nine products}

Substitute $\hat A_\alpha=\hat J_\alpha-\hat L_\alpha-\hat\pi_\alpha$ into (B.1) and multiply out, \emph{keeping the operator order} (the factors need not commute):
\begin{align}
\hat A_\alpha\mu_{\alpha\beta}\hat A_\beta
=\;&\underbrace{\hat J_\alpha\mu_{\alpha\beta}\hat J_\beta}_{\text{(T1) rotation}}
+\underbrace{\hat L_\alpha\mu_{\alpha\beta}\hat L_\beta}_{\text{(T2) electronic}}
+\underbrace{\hat\pi_\alpha\mu_{\alpha\beta}\hat\pi_\beta}_{\text{(T3) vibrational}}
-\underbrace{\bigl(\hat J_\alpha\mu_{\alpha\beta}\hat L_\beta+\hat L_\alpha\mu_{\alpha\beta}\hat J_\beta\bigr)}_{\text{(T4) rotation--electron}}\nonumber\\
&-\underbrace{\bigl(\hat J_\alpha\mu_{\alpha\beta}\hat\pi_\beta+\hat\pi_\alpha\mu_{\alpha\beta}\hat J_\beta\bigr)}_{\text{(T5) rotation--vibration}}
+\underbrace{\bigl(\hat L_\alpha\mu_{\alpha\beta}\hat\pi_\beta+\hat\pi_\alpha\mu_{\alpha\beta}\hat L_\beta\bigr)}_{\text{(T6) vibration--electron}} . \tag{B.6}
\end{align}
Each cross term collects the two equal classical contributions $X\mu Y$ and $Y\mu X$, which is why it appears as a symmetric sum of orderings. We now treat the six blocks one at a time: for each we verify Hermiticity and write the explicit differential form.

\subsubsection*{B.3\quad Diagonal terms}

\paragraph{(T1)\ \ $\hat J_\alpha\mu_{\alpha\beta}\hat J_\beta$.}
\emph{Hermiticity.} Take the adjoint ($\mu$ real, $\hat J_\alpha^\dagger=\hat J_\alpha$ on $\sin\theta\,d\Omega$; order reverses), then relabel the summed dummy indices $\alpha\leftrightarrow\beta$, then use $\mu_{\beta\alpha}=\mu_{\alpha\beta}$:
\begin{equation}
\bigl(\hat J_\alpha\mu_{\alpha\beta}\hat J_\beta\bigr)^{\dagger}
=\hat J_\beta\,\mu_{\alpha\beta}\,\hat J_\alpha
=\hat J_\alpha\,\mu_{\beta\alpha}\,\hat J_\beta
=\hat J_\alpha\,\mu_{\alpha\beta}\,\hat J_\beta . \tag{B.7}
\end{equation}
Hermitian exactly as written --- no symmetrization, no commutator evaluated. \emph{Differential form.} $\mu(Q)$ commutes with the Euler derivatives, and inserting (B.2),
\begin{equation}
\hat J_\alpha\mu_{\alpha\beta}\hat J_\beta
=-\hbar^{2}\mu_{\alpha\beta}\,(\mathsf E^{-1})_{s\alpha}\Bigl[(\mathsf E^{-1})_{t\beta}\,\partial_{\Omega_s}\partial_{\Omega_t}
+\bigl(\partial_{\Omega_s}(\mathsf E^{-1})_{t\beta}\bigr)\,\partial_{\Omega_t}\Bigr], \tag{B.8}
\end{equation}
with the trigonometric entries of $\mathsf E^{-1}$ read off (4.12). Every term carries at least one Euler derivative: the rotational block generates \emph{no} pure multiplicative term, in agreement with the block computation (4.29).

\paragraph{(T2)\ \ $\hat L_\alpha\mu_{\alpha\beta}\hat L_\beta$.}
Word-for-word the same as (T1) with $\hat J\to\hat L$: the adjoint chain (B.7) uses only $\hat L_\alpha^\dagger=\hat L_\alpha$ [(4.18)] and the symmetry of $\mu$. Hermitian as written; all terms carry electron derivatives; no multiplicative residue.

\paragraph{(T3)\ \ $\hat\pi_\alpha\mu_{\alpha\beta}\hat\pi_\beta$.}
\emph{Hermiticity.} Use $\hat\pi^{\dagger}=\hat\pi$ from (B.5), then relabel $\alpha\leftrightarrow\beta$ and use $\mu$ symmetric --- the same three-step chain as (B.7). Hermitian as written, but \emph{only} because $\hat\pi$ is Hermitian, i.e.\ ultimately because of the antisymmetry (B.4). \emph{Differential form.} Write $\hat\pi_\alpha=\sigma_{\alpha b}\hat P_b$ and slide the left momentum past the $Q$-function $\mu_{\alpha\beta}\sigma_{\beta c}$ with (B.3):
\begin{align}
\hat\pi_\alpha\mu_{\alpha\beta}\hat\pi_\beta
&=\sigma_{\alpha b}\,\hat P_b\,\bigl(\mu_{\alpha\beta}\sigma_{\beta c}\bigr)\,\hat P_c
=\sigma_{\alpha b}\Bigl[\bigl(\mu_{\alpha\beta}\sigma_{\beta c}\bigr)\hat P_b-i\hbar\,\partial_b\!\bigl(\mu_{\alpha\beta}\sigma_{\beta c}\bigr)\Bigr]\hat P_c\nonumber\\[2pt]
&=\underbrace{G_{bc}\,\hat P_b\hat P_c}_{\text{2nd order}}
\;-\;i\hbar\,\underbrace{\sigma_{\alpha b}\Bigl[(\partial_b\mu_{\alpha\beta})\sigma_{\beta c}+\mu_{\alpha\beta}\,\zeta^{\beta}_{bc}\Bigr]\hat P_c}_{\text{1st order}},
\qquad G_{bc}\equiv(\boldsymbol\sigma^{\mathsf T}\boldsymbol\mu\boldsymbol\sigma)_{bc}, \tag{B.9}
\end{align}
the Coriolis-dressed vibrational operator. Every surviving term carries at least one $\hat P$: again no pure multiplicative term. \emph{Equivalence with the ordered form.} The same sum rule shows that (T3) equals the fully left-ordered operator: moving the left $\hat P_b$ past its own coefficient $\sigma_{\alpha b}$,
\begin{equation}
\hat P_b\,G_{bc}\,\hat P_c
-\hat\pi_\alpha\mu_{\alpha\beta}\hat\pi_\beta
=\bigl[\hat P_b,\sigma_{\alpha b}\bigr]\,\mu_{\alpha\beta}\sigma_{\beta c}\hat P_c
=-i\hbar\Bigl(\textstyle\sum_b\zeta^{\alpha}_{bb}\Bigr)\mu_{\alpha\beta}\sigma_{\beta c}\hat P_c=0 , \tag{B.10}
\end{equation}
so $\tfrac12\hat\pi_\alpha\mu_{\alpha\beta}\hat\pi_\beta=\tfrac12\hat P_b\,G_{bc}\,\hat P_c$ \emph{exactly}. This identity is what lets the sandwich-ordered kernel of (4.41) match the vibrational block (4.31) of the Laplacian, whose dressed part is precisely $\tfrac12\hat P_bG_{bc}\hat P_c$ after the ordering of \S\,4.9 (see \S\,B.5).

\subsubsection*{B.4\quad Cross terms}

\paragraph{(T4)\ \ $\hat J_\alpha\mu_{\alpha\beta}\hat L_\beta+\hat L_\alpha\mu_{\alpha\beta}\hat J_\beta$.}
All three factors act on disjoint variables and mutually commute. A single ordering is already Hermitian,
\begin{equation}
\bigl(\hat J_\alpha\mu_{\alpha\beta}\hat L_\beta\bigr)^{\dagger}
=\hat L_\beta\,\mu_{\alpha\beta}\,\hat J_\alpha
=\mu_{\alpha\beta}\,\hat J_\alpha\hat L_\beta
=\hat J_\alpha\mu_{\alpha\beta}\hat L_\beta , \tag{B.11}
\end{equation}
and the two orderings in the sum are equal (relabel $\alpha\leftrightarrow\beta$ and commute), so
\begin{equation}
\hat J_\alpha\mu_{\alpha\beta}\hat L_\beta+\hat L_\alpha\mu_{\alpha\beta}\hat J_\beta
=2\,\mu_{\alpha\beta}\,\hat J_\alpha\hat L_\beta
\qquad(\text{Hermitian; no residue}). \tag{B.12}
\end{equation}
This is the rotation--electron Coriolis coupling; no $\hat P$ appears, so there is no differential subtlety.

\paragraph{(T5)\ \ $\hat J_\alpha\mu_{\alpha\beta}\hat\pi_\beta+\hat\pi_\alpha\mu_{\alpha\beta}\hat J_\beta$.}
Now the subtlety: $\hat\pi$ does \emph{not} commute with $\mu$, since by (B.3) $\hat\pi_\beta\mu_{\alpha\beta}=\mu_{\alpha\beta}\hat\pi_\beta-i\hbar\,\sigma_{\beta b}\partial_b\mu_{\alpha\beta}\neq\mu_{\alpha\beta}\hat\pi_\beta$. A single ordering is therefore \emph{not} Hermitian by itself; its adjoint is exactly the \emph{other} ordering ($\hat J$ commutes with $\mu$ and $\hat\pi$; relabel $\alpha\leftrightarrow\beta$):
\begin{equation}
\bigl(\hat J_\alpha\mu_{\alpha\beta}\hat\pi_\beta\bigr)^{\dagger}
=\hat\pi_\beta\,\mu_{\alpha\beta}\,\hat J_\alpha
=\hat\pi_\alpha\,\mu_{\alpha\beta}\,\hat J_\beta . \tag{B.13}
\end{equation}
The cross term is of the form $\hat X+\hat X^{\dagger}$, automatically Hermitian --- \emph{this is why the classical product $-2J\mu\pi$ must be quantized as the symmetric sum}, and it is precisely the symmetric sum that the expansion of the kinetic operator produced by itself in (4.30)/(4.35). Pulling $\hat J$ out front and expanding the anticommutator with (B.3),
\begin{equation}
\hat J_\alpha\mu_{\alpha\beta}\hat\pi_\beta+\hat\pi_\alpha\mu_{\alpha\beta}\hat J_\beta
=\hat J_\alpha\bigl(\mu_{\alpha\beta}\hat\pi_\beta+\hat\pi_\beta\mu_{\alpha\beta}\bigr)
=\hat J_\alpha\Bigl(\underbrace{2\,\mu_{\alpha\beta}\sigma_{\beta c}\hat P_c}_{\text{1st order in }\hat P}
\;\underbrace{-\,i\hbar\,\sigma_{\beta c}\,\partial_c\mu_{\alpha\beta}}_{\text{0th order in }\hat P}\Bigr). \tag{B.14}
\end{equation}
The first piece is the rotation--vibration Coriolis coupling ($\hat J$ times $\hat P$); the second is the imaginary, $\hat J$-linear counterterm that makes the sum Hermitian. It is \emph{not} a stand-alone multiplicative residue --- it still carries $\hat J_\alpha$ --- consistent with the result (4.35) that the Coriolis block contributes nothing to the pseudopotential. As a cross-check of (B.14) against the pre-reweighting form (4.30): expanding the second group of (4.30) by the product rule,
\begin{equation}
\tfrac{1}{\sqrt\gamma}\,\hat P_b\,\sqrt\gamma\;\sigma_{\alpha b}\mu_{\alpha\beta}\,\hat J_\beta
=\Bigl[\sigma_{\alpha b}\mu_{\alpha\beta}\hat P_b
-i\hbar\,\partial_b\!\bigl(\sigma_{\alpha b}\mu_{\alpha\beta}\bigr)
-\tfrac{i\hbar}{2}\,(\partial_b\ln\gamma)\,\sigma_{\alpha b}\mu_{\alpha\beta}\Bigr]\hat J_\beta , \tag{B.15}
\end{equation}
and conjugating by $\gamma^{1/4}$ as in \S\,4.9 cancels the $\partial_b\ln\gamma$ terms between the two groups, reproducing exactly $-\tfrac12\hat J_\alpha\{\mu_{\alpha\beta},\hat\pi_\beta\}$ of (4.35), i.e.\ $-\tfrac12\times$(B.14).

\paragraph{(T6)\ \ $\hat L_\alpha\mu_{\alpha\beta}\hat\pi_\beta+\hat\pi_\alpha\mu_{\alpha\beta}\hat L_\beta$.}
Identical to (T5) with $\hat J\to\hat L$ ($\hat L$ also commutes with $\mu$ and $\hat\pi$):
\begin{equation}
\hat L_\alpha\mu_{\alpha\beta}\hat\pi_\beta+\hat\pi_\alpha\mu_{\alpha\beta}\hat L_\beta
=\hat L_\alpha\Bigl(2\,\mu_{\alpha\beta}\sigma_{\beta c}\hat P_c-i\hbar\,\sigma_{\beta c}\,\partial_c\mu_{\alpha\beta}\Bigr), \tag{B.16}
\end{equation}
the vibration--electron angular coupling.

\subsubsection*{B.5\quad The measure residue $U_{\mathrm{Cor}}$, every derivative}

Section 4.9 derived the identity-block residue $U_{\mathrm{vib}}$ [(4.34)] in full and deferred the residue of the dressed block. Here it is. Order the dressed part of the vibrational block (4.31) --- i.e.\ conjugate it by $\gamma^{1/4}$, as dictated by the Podolsky sandwich (4.32$'$) --- and act on $\psi_W$; each line is one product rule [$G_{bc}=(\boldsymbol\sigma^{\mathsf T}\boldsymbol\mu\boldsymbol\sigma)_{bc}$, symmetric]:
\begin{align}
\partial_{Q_c}\!\bigl(\gamma^{-1/4}\psi_W\bigr)&=\gamma^{-1/4}\Bigl[\partial_{Q_c}\psi_W-\tfrac14(\partial_c\ln\gamma)\psi_W\Bigr],\nonumber\\
\gamma^{1/2}\,G_{bc}\,\partial_{Q_c}\!\bigl(\gamma^{-1/4}\psi_W\bigr)&=\gamma^{1/4}\,G_{bc}\Bigl[\partial_{Q_c}\psi_W-\tfrac14(\partial_c\ln\gamma)\psi_W\Bigr],\nonumber\\
\partial_{Q_b}\Bigl(\gamma^{1/4}\,G_{bc}\bigl[\cdots\bigr]\Bigr)
&=\gamma^{1/4}\Bigl[G_{bc}\,\partial_b\partial_c\psi_W+(\partial_bG_{bc})\,\partial_c\psi_W
+\tfrac14(\partial_b\ln\gamma)G_{bc}\,\partial_c\psi_W-\tfrac14 G_{bc}(\partial_c\ln\gamma)\,\partial_b\psi_W\nonumber\\
&\qquad\quad-\tfrac14\,\partial_b\bigl(G_{bc}\,\partial_c\ln\gamma\bigr)\psi_W
-\tfrac{1}{16}\,G_{bc}(\partial_b\ln\gamma)(\partial_c\ln\gamma)\,\psi_W\Bigr]. \tag{B.17}
\end{align}
The two first-order $\ln\gamma$ terms cancel by the symmetry of $G_{bc}$ (relabel $b\leftrightarrow c$), leaving $G\partial\partial+(\partial G)\partial$ --- which is exactly $-\tfrac{2}{\hbar^2}\times\tfrac12\hat P_bG_{bc}\hat P_c$ --- plus a pure multiplicative remainder. Multiplying by $-\tfrac{\hbar^2}{2}$ (the prefactors $\gamma^{1/4}\cdot\gamma^{-1/2}\cdot\gamma^{1/4}=1$ combine to unity),
\begin{equation}
\gamma^{1/4}\,\hat T_{\mathrm{dress}}\,\gamma^{-1/4}
=\tfrac12\,\hat P_b\,G_{bc}\,\hat P_c+U_{\mathrm{Cor}},\qquad
\boxed{\;U_{\mathrm{Cor}}=\frac{\hbar^{2}}{8}\Bigl[\partial_b\bigl(G_{bc}\,\partial_c\ln\gamma\bigr)+\tfrac14\,G_{bc}\,(\partial_b\ln\gamma)(\partial_c\ln\gamma)\Bigr].\;} \tag{B.18}
\end{equation}
By (B.10), $\tfrac12\hat P_bG_{bc}\hat P_c=\tfrac12\hat\pi_\alpha\mu_{\alpha\beta}\hat\pi_\beta$, so the operator part is exactly the (T3) sandwich of the kernel (4.41), and the entire ordering debt of the dressed block is the multiplicative $U_{\mathrm{Cor}}$. Together with $U_{\mathrm{vib}}$ of (4.34) [the same computation with $G_{bc}\to\delta_{bc}$], the total residue is
\begin{equation}
\hat U=U_{\mathrm{vib}}+U_{\mathrm{Cor}}
=\frac{\hbar^{2}}{8}\Bigl[\partial_b\bigl(g^{QQ}_{bc}\,\partial_c\ln\gamma\bigr)+\tfrac14\,g^{QQ}_{bc}\,(\partial_b\ln\gamma)(\partial_c\ln\gamma)\Bigr],
\qquad g^{QQ}_{bc}=\delta_{bc}+G_{bc}, \tag{B.19}
\end{equation}
the complete term-by-term collapse of (B.19) to the trace $\hat U=-\tfrac{\hbar^2}{8}\sum_\alpha\mu_{\alpha\alpha}$ of (4.38)~\cite{watson1968} --- via Jacobi's formula (4.36), Watson's closed form (4.37), and the Eckart sum rules --- is carried out in \S\,B.6.

\textbf{The division of labour is clean.} In the explicit forms (B.8), (B.9), (B.12), (B.14), (B.16), every surviving kernel term carries at least one derivative operator ($\hat P$, $\hat J$, or $\hat L$): \emph{the ordering of the kernel never generates a pure multiplicative term}. The pseudopotential (4.38) is an $\mathcal O(\hbar^2)$ $c$-number that originates entirely in the \emph{curved integration measure} $\sqrt\gamma$, extracted by the reweighting $\psi_W=\gamma^{1/4}\psi$ --- (B.18) is its dressed-block share. Kernel ordering $\rightarrow$ the Hermitian operators of this appendix; the measure $\rightarrow$ the pseudopotential.

\subsubsection*{B.6\quad From (B.19) to the Watson trace (4.38): every step}

Equation (B.19) expresses the total residue through two shape functions --- $\gamma=\det\mathbf I'$ and the Coriolis dressing $G_{bc}=(\boldsymbol\sigma^{\mathsf T}\boldsymbol\mu\boldsymbol\sigma)_{bc}$ --- and its collapse to the single trace (4.38) rests entirely on the \emph{Eckart sum rules}: completeness relations obeyed by the mode vectors $\mathbf l_{jb}$. This subsection derives each of them and then assembles (B.19) term by term. Throughout, $\Lambda_b\equiv\partial_{b}\ln\gamma$ with $\partial_b\equiv\partial_{Q_b}$, repeated indices are summed, and all matrices are $3\times3$ unless stated.

\paragraph{Step 0: expansion into five groups.}
In $\sum_{b}\partial_b(G_{bc}\Lambda_c)$ write $G_{bc}\Lambda_c=\sigma_{\alpha b}(\boldsymbol\mu\mathbf v)_\alpha$ with the 3-vector $v_\alpha\equiv\sum_c\sigma_{\alpha c}\Lambda_c$; the derivative of the explicit $\sigma_{\alpha b}$ dies by (B.4), $\sum_b\partial_b\sigma_{\alpha b}=\sum_b\zeta^\alpha_{bb}=0$. The product rule then splits (B.19) into five groups,
\begin{equation}
\frac{8}{\hbar^{2}}\,\hat U
=\underbrace{\sum_b\Bigl[\partial_b\Lambda_b+\tfrac14\Lambda_b^2\Bigr]}_{N_{0}}
+\underbrace{\sigma_{\alpha b}(\partial_b\boldsymbol\mu)_{\alpha\beta}\,v_\beta}_{N_{1}}
+\underbrace{\sigma_{\alpha b}\,\mu_{\alpha\beta}\,\zeta^{\beta}_{bc}\,\Lambda_c}_{N_{2}}
+\underbrace{G_{bc}\,\partial_b\Lambda_c}_{N_{3}}
+\underbrace{\tfrac14\,\mathbf v^{\mathsf T}\boldsymbol\mu\,\mathbf v}_{N_{4}} , \tag{B.20}
\end{equation}
where $N_1+N_2+N_3$ came from $\sigma_{\alpha b}\partial_b(\boldsymbol\mu\mathbf v)_\alpha$ via $\partial_b v_\beta=\zeta^{\beta}_{bc}\Lambda_c+\sigma_{\beta c}\,\partial_b\Lambda_c$. We now build the tools, evaluate each group, and add them up.

\paragraph{Step 1: the Eckart constants.}
Write $\mathbf e_j\equiv\sqrt{M_j}\,\bar{\mathbf R}^{\mathrm{eq}}_j$ and $\mathbf u_j(Q)\equiv\sqrt{M_j}\,\bar{\mathbf R}_j(Q)=\mathbf e_j+\sum_b\mathbf l_{jb}Q_b$, so that $\mathbf I_N=\sum_j(u_j^2\mathbb 1-\mathbf u_j\mathbf u_j^{\mathsf T})$ and $\sigma_{\alpha b}=\sum_j(\mathbf u_j\times\mathbf l_{jb})_\alpha$. Define the constants
\begin{equation}
S_{\alpha\beta}\equiv\sum_j e_{j\alpha}e_{j\beta},\qquad
\mathbf I^{e}=(\operatorname{tr}S)\,\mathbb 1-S,\qquad
\boldsymbol\mu^{e}\equiv(\mathbf I^{e})^{-1},\qquad
a^{b}_{\alpha\beta}\equiv\sum_j\bigl[2(\mathbf e_j\!\cdot\!\mathbf l_{jb})\delta_{\alpha\beta}-l_{jb,\alpha}e_{j\beta}-e_{j\alpha}l_{jb,\beta}\bigr], \tag{B.21}
\end{equation}
the $a^{b}$ being the equilibrium inertia derivatives, $a^b=\partial\mathbf I_N/\partial Q_b|_{Q=0}$. The rotational Eckart condition $\sum_j\mathbf e_j\times\mathbf l_{jb}=0$ says precisely that $E^{b}_{\alpha\beta}\equiv\sum_je_{j\alpha}l_{jb,\beta}$ is \emph{symmetric}; comparing with (B.21) and taking a trace,
\begin{equation}
E^{b}=s_b\,\mathbb 1-\tfrac12\,a^{b},\qquad
s_b\equiv\sum_j\mathbf e_j\!\cdot\!\mathbf l_{jb}=\tfrac14\operatorname{tr}a^{b}. \tag{B.22}
\end{equation}
Define $A(Q)\equiv\mathbf I^{e}+\tfrac12\sum_b a^{b}Q_b$ (symmetric, constant derivatives $\partial_cA=\tfrac12a^c$). Then (B.22) gives two exact corollaries used throughout [for the second: $\sum_bQ_bE^b=(\sum_bs_bQ_b)\mathbb 1-(A-\mathbf I^e)$ with $\sum_bs_bQ_b=\tfrac14\operatorname{tr}\!\sum_bQ_ba^b=\tfrac12\operatorname{tr}(A-\mathbf I^e)$, and $\operatorname{tr}\mathbf I^e=2\operatorname{tr}S$]:
\begin{equation}
\sum_bQ_b\,a^{b}=2\,(A-\mathbf I^{e}),
\qquad
Y_{\alpha\beta}\equiv\sum_ju_{j\alpha}e_{j\beta}=S_{\alpha\beta}+\sum_bQ_bE^b_{\alpha\beta}
=\tfrac12(\operatorname{tr}A)\,\delta_{\alpha\beta}-A_{\alpha\beta}. \tag{B.23}
\end{equation}

\paragraph{Step 2: completeness and the two workhorse contractions.}
The $3N_{\mathrm{nucl}}$ mass-weighted displacement vectors --- the $f$ vibrations $\mathbf l_{b}$, three translations $\propto\sqrt{M_j}\,\hat{\mathbf n}_\alpha$, and three rotations $t^{\gamma}_{j\beta}=(\hat{\mathbf n}_\gamma\times\mathbf e_j)_\beta$ (mutually orthogonal by the Eckart conditions; rotational Gram matrix $\sum_j\mathbf t^{\gamma}_j\!\cdot\!\mathbf t^{\delta}_j=I^{e}_{\gamma\delta}$) --- form a complete set. Resolving the identity on $\mathbb R^{3N_{\mathrm{nucl}}}$,
\begin{equation}
\sum_b l_{jb,\alpha}\,l_{kb,\beta}
=\delta_{jk}\delta_{\alpha\beta}
-\frac{\sqrt{M_jM_k}}{M_N}\,\delta_{\alpha\beta}
-\epsilon_{\gamma\rho\alpha}\,e_{j\rho}\;\mu^{e}_{\gamma\delta}\;\epsilon_{\delta\sigma\beta}\,e_{k\sigma}. \tag{B.24}
\end{equation}
Every contraction below pairs (B.24) with coefficients built from $\mathbf e_j$, $\mathbf u_j$, or $\mathbf l_{jc}$, all orthogonal to the translations ($\sum_j\sqrt{M_j}\,\mathbf e_j=\sum_j\sqrt{M_j}\,\mathbf u_j=\sum_j\sqrt{M_j}\,\mathbf l_{jc}=0$), so \emph{the translational term never contributes}. The rotational term always meets one of two $\epsilon$-contractions, evaluated once and for all with $\epsilon_{\alpha\gamma\delta}\epsilon_{\gamma''\rho\delta}=\delta_{\alpha\gamma''}\delta_{\gamma\rho}-\delta_{\alpha\rho}\delta_{\gamma\gamma''}$, (B.22), and (B.23):
\begin{equation}
\epsilon_{\alpha\gamma\delta}\,\epsilon_{\gamma''\rho\delta}\sum_j l_{jc,\gamma}\,e_{j\rho}
=s_c\,\delta_{\alpha\gamma''}-E^{c}_{\alpha\gamma''}=\tfrac12\,a^{c}_{\alpha\gamma''},
\qquad
\epsilon_{\alpha\gamma\delta}\,\epsilon_{\gamma''\rho\delta}\sum_j u_{j\gamma}\,e_{j\rho}
=\tfrac12(\operatorname{tr}A)\,\delta_{\alpha\gamma''}-Y_{\gamma''\alpha}=A_{\alpha\gamma''}. \tag{B.25}
\end{equation}

\paragraph{Step 3: the four sum rules.}
Insert (B.24) into each vibrational-index contraction and evaluate the rotational corrections with (B.25). For the $\zeta\zeta$ contraction, $\zeta^\alpha_{bd}\zeta^\beta_{cd}=\epsilon_{\alpha\gamma\delta}\epsilon_{\beta\varepsilon\varphi}\sum_{jk}l_{jb,\gamma}l_{kc,\varepsilon}\,[\sum_d l_{jd,\delta}l_{kd,\varphi}]$: the $\delta_{jk}$ part contracts the two $\epsilon$'s directly, the rotational part produces $\tfrac12a^b$ on each side, giving
\begin{equation}
\sum_d\zeta^{\alpha}_{bd}\,\zeta^{\beta}_{cd}
=\delta_{\alpha\beta}\,\delta_{bc}-\sum_jl_{jb,\beta}\,l_{jc,\alpha}
-\tfrac14\bigl(a^{b}\boldsymbol\mu^{e}a^{c}\bigr)_{\alpha\beta}. \tag{B.26}
\end{equation}
By the same pattern (the $\mathbf u$-side of a $\boldsymbol\sigma$ produces $A$, an $\mathbf l$- or $a$-side produces $\tfrac12a$), with the shorthand
\begin{equation}
V[M]^{\alpha}_{\gamma\delta}\equiv\epsilon_{\alpha\rho\gamma}M_{\rho\delta}+\epsilon_{\alpha\rho\delta}M_{\rho\gamma}
\quad(\text{any symmetric }M;\ V[\mathbb 1]=0), \tag{B.27}
\end{equation}
one finds the $aa$, $\sigma a$, and $\sigma\zeta$ rules
\begin{align}
\sum_b a^{b}_{yz}\,a^{b}_{wx}
&=4(\operatorname{tr}S)\delta_{yz}\delta_{wx}-4S_{wx}\delta_{yz}-4S_{yz}\delta_{wx}
+\delta_{yw}S_{zx}+\delta_{yx}S_{zw}+\delta_{zw}S_{yx}+\delta_{zx}S_{yw}\nonumber\\
&\qquad-V[S]^{\gamma}_{yz}\,\mu^{e}_{\gamma\delta}\,V[S]^{\delta}_{wx}, \tag{B.28}\\[2pt]
\sum_b\sigma_{\alpha b}\,a^{b}_{\gamma\delta}
&=V[A]^{\alpha}_{\gamma\delta}+(A\boldsymbol\mu^{e})_{\alpha\varepsilon}\,V[S]^{\varepsilon}_{\gamma\delta}, \tag{B.29}\\[2pt]
\sum_b\sigma_{\alpha b}\,\zeta^{\beta}_{bc}
&=\sum_ju_{j\beta}\,l_{jc,\alpha}-\delta_{\alpha\beta}\,(s_c+Q_c)+\tfrac12\bigl(A\boldsymbol\mu^{e}a^{c}\bigr)_{\alpha\beta}. \tag{B.30}
\end{align}

\paragraph{Step 4: Watson's closed form for $\mathbf I'$ [the identity (4.37)].}
Expand $\mathbf I_N$ and $\boldsymbol\sigma\boldsymbol\sigma^{\mathsf T}$ exactly (both are quadratic polynomials in $Q$; the linear coefficient of $\mathbf I_N$ is $a^b$ by (B.22)):
\begin{equation}
\mathbf I_{N,\alpha\beta}=\mathbf I^{e}_{\alpha\beta}+\sum_ba^{b}_{\alpha\beta}Q_b
+\sum_{b,c}Q_bQ_c\Bigl[\delta_{bc}\delta_{\alpha\beta}-\sum_jl_{jb,\alpha}l_{jc,\beta}\Bigr],
\qquad
(\boldsymbol\sigma\boldsymbol\sigma^{\mathsf T})_{\alpha\beta}=\sum_{b,c}Q_bQ_c\sum_d\zeta^{\alpha}_{bd}\zeta^{\beta}_{cd}. \tag{B.31}
\end{equation}
Subtracting and inserting (B.26), the $\delta$-terms cancel, the two $\sum_jl\,l$ terms cancel under the $b\!\leftrightarrow\!c$ symmetrization enforced by $Q_bQ_c$, and only the $\tfrac14a^b\boldsymbol\mu^{e}a^c$ term survives --- which is exactly the quadratic term of $A\boldsymbol\mu^{e}A$:
\begin{equation}
\boxed{\;\mathbf I'(Q)=A(Q)\,\boldsymbol\mu^{e}A(Q),\qquad A(Q)=\mathbf I^{e}+\tfrac12\sum_ba^{b}Q_b ,\;} \tag{B.32}
\end{equation}
the closed form quoted as (4.37). Its corollaries do all the differential work below:
\begin{equation}
\boldsymbol\mu=A^{-1}\mathbf I^{e}A^{-1},\qquad
\boldsymbol\mu A=A^{-1}\mathbf I^{e},\qquad
A\boldsymbol\mu A=\mathbf I^{e},\qquad
\boldsymbol\mu A\boldsymbol\mu^{e}=A^{-1},\qquad
\gamma=\frac{(\det A)^{2}}{\det\mathbf I^{e}} , \tag{B.33}
\end{equation}
and hence, with $B^{b}\equiv A^{-1}a^{b}$ and Jacobi's formula (4.36) applied to $\det A$,
\begin{equation}
\Lambda_b=\partial_b\ln\gamma=2\operatorname{tr}\bigl(A^{-1}\partial_bA\bigr)=\operatorname{tr}B^{b},
\qquad
\partial_c\Lambda_b=-\tfrac12\operatorname{tr}\bigl(B^{b}B^{c}\bigr): \tag{B.34}
\end{equation}
every derivative of $\gamma$ and $\boldsymbol\mu$ reduces to the \emph{constant} matrices $a^{b}$.

\paragraph{Step 5: the identity group $N_0$.}
By (B.34), $N_0=\sum_b[-\tfrac12\operatorname{tr}(B^bB^b)+\tfrac14(\operatorname{tr}B^b)^2]$. Both sums are contractions of (B.28) with two factors of $A^{-1}$; carrying them out term by term (each Kronecker term becomes a trace) and writing $\kappa_\gamma\equiv\epsilon_{\gamma\sigma\tau}(SA^{-1})_{\sigma\tau}=\tfrac12\operatorname{tr}(A^{-1}V[S]^{\gamma})$ for the antisymmetric part of $SA^{-1}$:
\begin{align}
N_0=\;&\operatorname{tr}S\,\bigl[(\operatorname{tr}A^{-1})^{2}-2\operatorname{tr}A^{-2}\bigr]
+4\operatorname{tr}(A^{-2}S)-3\operatorname{tr}(A^{-1})\operatorname{tr}(A^{-1}S)\nonumber\\
&+\tfrac12\,\mu^{e}_{\gamma\delta}\operatorname{tr}\bigl(A^{-1}V[S]^{\gamma}A^{-1}V[S]^{\delta}\bigr)
-\boldsymbol\kappa^{\mathsf T}\boldsymbol\mu^{e}\boldsymbol\kappa . \tag{B.35}
\end{align}

\paragraph{Step 6: $N_1$ vanishes (a divergence lemma).}
From (B.33), $\partial_b\boldsymbol\mu=-\tfrac12(B^{b}\boldsymbol\mu+\boldsymbol\mu B^{b\mathsf T})$, so $N_1$ needs $\sum_b\sigma_{\alpha b}B^{b}_{\alpha q}$ and $\sum_b\sigma_{\alpha b}(\boldsymbol\mu B^{b\mathsf T})_{\alpha r}$, both fixed by (B.29). Each vanishes identically: $A^{-1}_{\alpha p}V[A]^{\alpha}_{pq}=0$ and $\mu_{\alpha p}V[A]^{\alpha}_{pq}$-type contractions reduce, via $A^{-1}A=\mathbb 1$, $\boldsymbol\mu A\boldsymbol\mu^{e}=A^{-1}$, and the commutativity of $S$ with $\mu^{e}$ (both are functions of $S$), to $\epsilon$-contractions of \emph{symmetric} matrices, which are zero, plus a pair $\pm\kappa_r$ that cancels. Hence
\begin{equation}
\sum_b\sigma_{\alpha b}\,(\partial_b\boldsymbol\mu)_{\alpha\beta}=0
\qquad\Longleftrightarrow\qquad
\sum_b\partial_b\,(\boldsymbol\mu\boldsymbol\sigma)_{\alpha b}=0,
\qquad\text{so}\qquad N_1=0 : \tag{B.36}
\end{equation}
the three vector fields $(\boldsymbol\mu\boldsymbol\sigma)_{\alpha b}$ are divergence-free on the mode space.

\paragraph{Step 7: the quadratic group $N_4$.}
Contracting (B.29) with $A^{-1}$ gives $v_\alpha=\sum_b\sigma_{\alpha b}\operatorname{tr}B^b$: the $V[A]$ part dies [$\operatorname{tr}(A^{-1}V[A]^{\alpha})=0$ by the same symmetric-$\epsilon$ argument], leaving $v_\alpha=2(A\boldsymbol\mu^{e}\boldsymbol\kappa)_\alpha$. Then, by $A\boldsymbol\mu A=\mathbf I^{e}$,
\begin{equation}
N_4=\tfrac14\,\mathbf v^{\mathsf T}\boldsymbol\mu\,\mathbf v
=\boldsymbol\kappa^{\mathsf T}\boldsymbol\mu^{e}\,(A\boldsymbol\mu A)\,\boldsymbol\mu^{e}\boldsymbol\kappa
=\boldsymbol\kappa^{\mathsf T}\boldsymbol\mu^{e}\boldsymbol\kappa , \tag{B.37}
\end{equation}
which cancels the last term of (B.35) on the spot.

\paragraph{Step 8: the Coriolis-dressed group $N_3$.}
By (B.34), $N_3=-\tfrac12\,G_{bc}\operatorname{tr}(B^bB^c)=-\tfrac12\,\mu_{\alpha\beta}\operatorname{tr}\bigl(A^{-1}W_\alpha A^{-1}W_\beta\bigr)$ with $W_\alpha\equiv\sum_b\sigma_{\alpha b}a^b$ from (B.29). Expanding $W=V[A]+A\boldsymbol\mu^{e}V[S]$ and using $\boldsymbol\mu(A\boldsymbol\mu^{e})=A^{-1}$ and $(A\boldsymbol\mu^{e})^{\mathsf T}\boldsymbol\mu(A\boldsymbol\mu^{e})=\boldsymbol\mu^{e}$:
\begin{equation}
N_3=-\tfrac12\,\mu_{\alpha\beta}\operatorname{tr}\bigl(A^{-1}V[A]^{\alpha}A^{-1}V[A]^{\beta}\bigr)
-A^{-1}_{\alpha\varepsilon}\operatorname{tr}\bigl(A^{-1}V[A]^{\alpha}A^{-1}V[S]^{\varepsilon}\bigr)
-\tfrac12\,\mu^{e}_{\varepsilon\varphi}\operatorname{tr}\bigl(A^{-1}V[S]^{\varepsilon}A^{-1}V[S]^{\varphi}\bigr) , \tag{B.38}
\end{equation}
whose last term cancels the $\mu^{e}$-quadratic term of (B.35). All $\boldsymbol\mu^{e}$-dependence is now gone from the running total.

\paragraph{Step 9: the mixed group $N_2$.}
Contract (B.30) with $\mu_{\alpha\beta}\Lambda_c$. Three auxiliary sums close the two non-constant pieces. First, contracting (B.24) once more [with the coefficients of $s_c$ and of $\Lambda_c$; the rotational corrections vanish by symmetry of $S$],
\begin{equation}
\sum_c s_c\,a^{c}=2\,\mathbf I^{e}
\quad\Longrightarrow\quad
\sum_c(s_c+Q_c)\Lambda_c
=\operatorname{tr}\Bigl(A^{-1}\bigl[2\mathbf I^{e}+2(A-\mathbf I^{e})\bigr]\Bigr)=6 . \tag{B.39}
\end{equation}
Second, the same completeness argument applied to $\ell_{j\alpha}\equiv\sum_cl_{jc,\alpha}\Lambda_c$ and to $P\equiv\sum_c\Lambda_c\,a^{c}$ [a contraction of (B.28)] gives
\begin{equation}
\ell_{j\alpha}=2\bigl[(\operatorname{tr}A^{-1})\,e_{j\alpha}-(A^{-1}\mathbf e_j)_{\alpha}\bigr]+2\,\epsilon_{\gamma\rho\alpha}\,e_{j\rho}\,(\boldsymbol\mu^{e}\boldsymbol\kappa)_{\gamma}\, ,
\qquad
\tfrac12\operatorname{tr}\bigl(A^{-1}P\bigr)
=2\operatorname{tr}S(\operatorname{tr}A^{-1})^{2}-4\operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)+2\operatorname{tr}(A^{-2}S)-2\boldsymbol\kappa^{\mathsf T}\boldsymbol\mu^{e}\boldsymbol\kappa . \tag{B.40}
\end{equation}
Assembling [$\sum_ju_{j\beta}l_{jc,\alpha}$ contracts to $\sum_j(\boldsymbol\mu\mathbf u_j)\cdot\boldsymbol\ell_j$, evaluated with $Y=\tfrac12(\operatorname{tr}A)\mathbb 1-A$ of (B.23) and $\operatorname{tr}(A^{-1}\boldsymbol\mu A)=\operatorname{tr}\boldsymbol\mu$; the term $-\delta_{\alpha\beta}(s_c+Q_c)$ contributes $-6\operatorname{tr}\boldsymbol\mu$ by (B.39); the last term of (B.30) contributes $\tfrac12\operatorname{tr}(A^{-1}P)$ via $\boldsymbol\mu A\boldsymbol\mu^{e}=A^{-1}$; the two $\boldsymbol\kappa^{\mathsf T}\boldsymbol\mu^{e}\boldsymbol\kappa$ terms cancel between $\boldsymbol\ell_j$ and $P$]:
\begin{equation}
N_2=\operatorname{tr}A\,\bigl[\operatorname{tr}A^{-1}\operatorname{tr}\boldsymbol\mu-\operatorname{tr}(A^{-1}\boldsymbol\mu)\bigr]
-2\operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)-4\operatorname{tr}\boldsymbol\mu+2\operatorname{tr}(A^{-2}S) . \tag{B.41}
\end{equation}

\paragraph{Step 10: the two remaining $\epsilon$-traces.}
The $V$-traces left in (B.38) are evaluated with the pair identity (any symmetric $M$)
\begin{equation}
M_{ij}\,\epsilon_{iab}\,\epsilon_{jcd}
=\operatorname{tr}M(\delta_{ac}\delta_{bd}-\delta_{ad}\delta_{bc})
-M_{ac}\delta_{bd}+M_{bc}\delta_{ad}+M_{ad}\delta_{bc}-M_{bd}\delta_{ac} , \tag{B.42}
\end{equation}
together with $A^{-1}A=\mathbb 1$ (which collapses every $V[A]$ factor). The results are
\begin{align}
\mu_{\alpha\beta}\operatorname{tr}\bigl(A^{-1}V[A]^{\alpha}A^{-1}V[A]^{\beta}\bigr)
&=2\operatorname{tr}A\,\bigl[\operatorname{tr}A^{-1}\operatorname{tr}\boldsymbol\mu-\operatorname{tr}(A^{-1}\boldsymbol\mu)\bigr]
-6\operatorname{tr}\boldsymbol\mu-2\operatorname{tr}A^{-1}\bigl[\operatorname{tr}S\operatorname{tr}A^{-1}-\operatorname{tr}(A^{-1}S)\bigr], \tag{B.43}\\
A^{-1}_{\alpha\varepsilon}\operatorname{tr}\bigl(A^{-1}V[A]^{\alpha}A^{-1}V[S]^{\varepsilon}\bigr)
&=2\operatorname{tr}S\,\bigl[(\operatorname{tr}A^{-1})^{2}-\operatorname{tr}A^{-2}\bigr]
-6\operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)+6\operatorname{tr}(A^{-2}S) . \tag{B.44}
\end{align}

\paragraph{Step 11: assembly.}
Add the five groups. The $\boldsymbol\kappa^{\mathsf T}\boldsymbol\mu^{e}\boldsymbol\kappa$ terms cancelled between (B.35) and (B.37); the $\mu^{e}$-quadratic $V[S]$ traces cancelled between (B.35) and (B.38); the $\operatorname{tr}A[\cdots]$ terms cancel between (B.41) and the first line of (B.43). What remains is a short list of ordinary traces:
\begin{align}
\frac{8}{\hbar^{2}}\hat U
=\;&\underbrace{\operatorname{tr}S\bigl[(\operatorname{tr}A^{-1})^{2}-2\operatorname{tr}A^{-2}\bigr]+4\operatorname{tr}(A^{-2}S)-3\operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)}_{\text{from }N_0}
\underbrace{-\,2\operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)-4\operatorname{tr}\boldsymbol\mu+2\operatorname{tr}(A^{-2}S)}_{\text{from }N_2}\nonumber\\
&\underbrace{+\,3\operatorname{tr}\boldsymbol\mu+\operatorname{tr}S(\operatorname{tr}A^{-1})^{2}-\operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)}_{\text{from }-\frac12\times\text{(B.43)}}
\underbrace{-\,2\operatorname{tr}S\bigl[(\operatorname{tr}A^{-1})^{2}-\operatorname{tr}A^{-2}\bigr]+6\operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)-6\operatorname{tr}(A^{-2}S)}_{\text{from }-\text{(B.44)}}\nonumber\\
=\;&-\operatorname{tr}\boldsymbol\mu\qquad
\bigl[\text{all }(\operatorname{tr}A^{-1})^{2},\ \operatorname{tr}A^{-2},\ \operatorname{tr}(A^{-2}S),\ \operatorname{tr}A^{-1}\operatorname{tr}(A^{-1}S)\text{ coefficients vanish};\ \operatorname{tr}\boldsymbol\mu=\operatorname{tr}S\operatorname{tr}A^{-2}-\operatorname{tr}(A^{-2}S)\bigr], \tag{B.45}
\end{align}
that is,
\begin{equation}
\boxed{\;\hat U(Q)=-\frac{\hbar^{2}}{8}\sum_{\alpha}\mu_{\alpha\alpha}(Q)\;}\tag{B.46}
\end{equation}
--- Watson's trace formula (4.38), obtained from (B.19) using only the product rule, Jacobi's formula, and the Eckart completeness relation (B.24). No commutator of body-fixed angular momenta was used at any step.

\subsubsection*{B.7\quad Worked example: a bent triatomic}

To make ``every derivative'' concrete, take a bent triatomic $XY_2$ (e.g.\ H${}_2$O), a $C_{2v}$ asymmetric top with $N_{\mathrm{nucl}}=3$ and $f=3N_{\mathrm{nucl}}-6=3$ normal coordinates: the symmetric stretch $Q_1$ and bend $Q_2$ (both $a_1$) and the antisymmetric stretch $Q_3$ ($b_2$). Choose the body frame as the instantaneous principal-axis system, with $a,b$ in the molecular plane and $c\perp$ to it.

\paragraph{Inertia and its derivatives.}
At equilibrium the inertia tensor is diagonal, $\mathbf I_N^{\mathrm{eq}}=\operatorname{diag}(I_a^{e},I_b^{e},I_c^{e})$, and because the equilibrium mass distribution is planar the perpendicular-axis theorem gives the exact relation
\begin{equation}
I_c^{e}=I_a^{e}+I_b^{e}. \tag{B.47}
\end{equation}
The totally symmetric coordinates $Q_1,Q_2$ preserve the $C_{2v}$ symmetry, so to linear order they only \emph{scale} the diagonal moments, whereas the antisymmetric $Q_3$ tilts the principal axes and enters $\mathbf I_N$ only at second order. Hence
\begin{equation}
I_\alpha(Q)=I_\alpha^{e}+a_\alpha^{1}Q_1+a_\alpha^{2}Q_2+\mathcal O(Q^2),
\qquad a_\alpha^{b}\equiv\frac{\partial I_\alpha}{\partial Q_b}\Big|_{\mathrm{eq}}, \tag{B.48}
\end{equation}
with the inertial derivatives $a_\alpha^{b}$ computable from the mode vectors $\mathbf l_{jb}$ evaluated at equilibrium. These are exactly the derivatives that populate the rotation--vibration Jacobian $\sqrt{\gamma(Q)}$ of (4.21).

\paragraph{Coriolis coupling.}
The only nonzero constant Coriolis matrix in $C_{2v}$ couples the two $a_1$ modes to the $b_2$ mode about the $b$ axis (the axis whose rotation maps a symmetric into an antisymmetric displacement):
\begin{equation}
\boldsymbol\sigma_1=\zeta^{b}_{13}\,Q_3\,\hat{\mathbf b},\quad
\boldsymbol\sigma_2=\zeta^{b}_{23}\,Q_3\,\hat{\mathbf b},\quad
\boldsymbol\sigma_3=-\bigl(\zeta^{b}_{13}Q_1+\zeta^{b}_{23}Q_2\bigr)\hat{\mathbf b},
\qquad \zeta^{b}_{ab}=-\zeta^{b}_{ba}, \tag{B.49}
\end{equation}
so $\boldsymbol\sigma\boldsymbol\sigma^{T}=\bigl[(\zeta^{b}_{13}Q_3)^2+(\zeta^{b}_{23}Q_3)^2+(\zeta^{b}_{13}Q_1+\zeta^{b}_{23}Q_2)^2\bigr]\hat{\mathbf b}\hat{\mathbf b}^{T}$ corrects only the $bb$ element of the inertia,
\begin{equation}
\mathbf I'(Q)=\operatorname{diag}\!\bigl(I_a(Q),\,I_b(Q)-s(Q),\,I_c(Q)\bigr),\qquad
s(Q)\equiv(\zeta^{b}_{13}Q_3)^2+(\zeta^{b}_{23}Q_3)^2+(\zeta^{b}_{13}Q_1+\zeta^{b}_{23}Q_2)^2 . \tag{B.50}
\end{equation}
Note $s(Q)=\mathcal O(Q^2)$, so it does not affect the linear-order derivatives (B.48) but does enter the pseudopotential and the exact Jacobian.

\paragraph{Determinant, volume element, and its explicit derivatives.}
With $\mathbf I'$ diagonal in (B.50),
\begin{equation}
\gamma(Q)=\det\mathbf I'=I_a(Q)\,\bigl(I_b(Q)-s(Q)\bigr)\,I_c(Q),\qquad
\sqrt{g}=\sin\theta\,\sqrt{I_a\,(I_b-s)\,I_c}, \tag{B.51}
\end{equation}
and the vibrational Jacobian carries the explicit derivatives
\begin{equation}
\partial_{Q_b}\ln\gamma
=\frac{a_a^{b}}{I_a}+\frac{a_b^{b}-\partial_{Q_b}s}{I_b-s}+\frac{a_c^{b}}{I_c},
\qquad
\partial_{Q_3}s=2\bigl[(\zeta^{b}_{13})^2+(\zeta^{b}_{23})^2\bigr]Q_3,\;\;
\partial_{Q_1}s=2\zeta^{b}_{13}\bigl(\zeta^{b}_{13}Q_1+\zeta^{b}_{23}Q_2\bigr),\ \text{etc.}, \tag{B.52}
\end{equation}
which are precisely the first-order remainders exhibited under (4.31) and removed by the $\gamma^{1/4}$ reweighting of \S\,4.9.

\paragraph{Pseudopotential.}
Since $\mathbf I'$ is diagonal, $\boldsymbol\mu=\operatorname{diag}\bigl(1/I_a,\,1/(I_b-s),\,1/I_c\bigr)$ and the trace formula (4.38) is fully explicit:
\begin{equation}
\boxed{\;\hat U(Q)=-\frac{\hbar^2}{8}\Bigl[\frac{1}{I_a(Q)}+\frac{1}{I_b(Q)-s(Q)}+\frac{1}{I_c(Q)}\Bigr].\;}\tag{B.53}
\end{equation}
Expanding to the order at which it first varies with the coordinates, and using (B.47),
\begin{equation}
\hat U(Q)=-\frac{\hbar^2}{8}\Bigl(\frac{1}{I_a^{e}}+\frac{1}{I_b^{e}}+\frac{1}{I_c^{e}}\Bigr)
+\frac{\hbar^2}{8}\sum_{b=1,2}\Bigl(\frac{a_a^{b}}{(I_a^{e})^2}+\frac{a_b^{b}}{(I_b^{e})^2}+\frac{a_c^{b}}{(I_c^{e})^2}\Bigr)Q_b+\mathcal O(Q^2). \tag{B.54}
\end{equation}
The constant is an inconsequential shift of the electronic--vibrational zero; the linear term is a genuine $\hbar^2$ force on the normal coordinates --- the physical content of the Watson pseudopotential for this molecule --- produced entirely by differentiating $\sqrt{\gamma(Q)}$ through (B.52). Every step from the metric (4.15) to the surface (B.54) used only $\partial_\phi,\partial_\theta,\partial_\chi$ and $\partial_{Q_b}$.

\subsubsection*{B.8\quad Summary}

\begin{enumerate}
\item The quantized kernel (B.1) expands into the nine products (B.6). Blocks built from mutually commuting, individually Hermitian factors --- (T1) $\hat J\mu\hat J$, (T2) $\hat L\mu\hat L$, (T4) $\hat J\mu\hat L$ --- are Hermitian in a single ordering, by the adjoint-reversal argument (B.7) alone.
\item Blocks pairing $\hat\pi$ with $\hat J$ or $\hat L$ --- (T5), (T6) --- are Hermitian only as the symmetric sum $\hat X+\hat X^\dagger$, which is exactly the ordering Podolsky's sandwich (4.32$'$) produces by itself [(4.30), (4.35)]. (T3) $\hat\pi\mu\hat\pi$ is the fortunate middle case, Hermitian because $\hat\pi$ is [(B.5)], and equal to the left-ordered $\tfrac12\hat P G\hat P$ by the sum rule (B.10).
\item No kernel ordering produces a pure multiplicative term. The Watson pseudopotential comes solely from the measure: $U_{\mathrm{vib}}$ [(4.34)] plus $U_{\mathrm{Cor}}$ [(B.18)] collapse to $-\tfrac{\hbar^2}{8}\sum_\alpha\mu_{\alpha\alpha}$ [(4.38)].
\item Every Hermiticity statement above used only integration by parts, the product rule, and the divergence identities (4.18), (4.26), (B.4) --- never a commutator of body-fixed angular momenta.
\end{enumerate}
